PANCHANGE_analysis

### 2020-11-19 PANCHANGE_analysis.Rmd

@@

# OCIR retro
## Regression: Change scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r ocir model0a diff_score retro}
# Regression coefficients
ocir_retro_model0a_estimates <- model0a.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model0a_estimates)
ocir_retro_model0a_estimates

@@

@@

# Regression diagnostic statistics
ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_reg_stats)
ocir_retro_model1b_explan_reg_stats
```

@@

@@

@@

# SENSITIVITY based on highest level of education

>>>>

### Model 2a: Disorder hierarchical, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r ocir model2a diff_score prepan}
# Regression coefficients
ocir_prepan_model2a_estimates <- model2a.estimates(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan_age_sensitivity")
kable(ocir_prepan_model2a_estimates)
ocir_prepan_model2a_estimates

# Regression diagnostic statistics
ocir_prepan_model2a_reg_stats <- model2a.reg.stats(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan_age_sensitivity")
kable(ocir_prepan_model2a_reg_stats)
ocir_prepan_model2a_reg_stats
```

### Model 2b: Overlapping disorders, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r ocir model2b diff_score prepan}
# Regression coefficients
ocir_prepan_model2b_estimates <- model2b.estimates(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan_age_sensitivity")
kable(ocir_prepan_model2b_estimates)
ocir_prepan_model2b_estimates

# Regression diagnostic statistics
ocir_prepan_model2b_reg_stats <- model2b.reg.stats(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan_age_sensitivity")
kable(ocir_prepan_model2b_reg_stats)
ocir_prepan_model2b_reg_stats
```

@@

### Model 2a: Disorder hierarchical, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r ocir model2a sum_score prepan}
# Regression coefficients
ocir_prepan_model2a_explan_estimates <- model2a.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan_age_sensitivity")
kable(ocir_prepan_model2a_explan_estimates)
ocir_prepan_model2a_explan_estimates

# Regression diagnostic statistics
ocir_prepan_model2a_explan_reg_stats <- model2a.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan_age_sensitivity")
kable(ocir_prepan_model2a_explan_reg_stats)
ocir_prepan_model2a_explan_reg_stats
```

### Model 2b: Overlapping disorders, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r ocir model2b sum_score prepan}
# Regression coefficients
ocir_prepan_model2b_explan_estimates <- model2b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan_age_sensitivity")
kable(ocir_prepan_model2b_explan_estimates)
ocir_prepan_model2b_explan_estimates

# Regression diagnostic statistics
ocir_prepan_model2b_explan_reg_stats <- model2b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan_age_sensitivity")
kable(ocir_prepan_model2b_explan_reg_stats)
ocir_prepan_model2b_explan_reg_stats
```
# OCIR retro
## Regression: Change scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r ocir model0a diff_score retro}
# Regression coefficients
ocir_retro_model0a_estimates <- model0a.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model0a_estimates)
ocir_retro_model0a_estimates

@@

### Model 2a: Disorder hierarchical, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r ocir model2a diff_score retro}
# Regression coefficients
ocir_retro_model2a_estimates <- model2a.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_age_sensitivity")
kable(ocir_retro_model2a_estimates)
ocir_retro_model2a_estimates

# Regression diagnostic statistics
ocir_retro_model2a_reg_stats <- model2a.reg.stats(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_age_sensitivity")
kable(ocir_retro_model2a_reg_stats)
ocir_retro_model2a_reg_stats
```

### Model 2b: Overlapping disorders, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r ocir model2b diff_score retro}
# Regression coefficients
ocir_retro_model2b_estimates <- model2b.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_age_sensitivity")
kable(ocir_retro_model2b_estimates)
ocir_retro_model2b_estimates

# Regression diagnostic statistics
ocir_retro_model2b_reg_stats <- model2b.reg.stats(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_age_sensitivity")
kable(ocir_retro_model2b_reg_stats)
ocir_retro_model2b_reg_stats
```

@@

# Regression diagnostic statistics
ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_reg_stats)
ocir_retro_model1b_explan_reg_stats
```
### Model 2a: Disorder hierarchical, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r ocir model2a sum_score retro}
# Regression coefficients
ocir_retro_model2a_explan_estimates <- model2a.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_age_sensitivity")
kable(ocir_retro_model2a_explan_estimates)
ocir_retro_model2a_explan_estimates

# Regression diagnostic statistics
ocir_retro_model2a_explan_reg_stats <- model2a.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_age_sensitivity")
kable(ocir_retro_model2a_explan_reg_stats)
ocir_retro_model2a_explan_reg_stats
```

### Model 2b: Overlapping disorders, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r ocir model2b sum_score retro}
# Regression coefficients
ocir_retro_model2b_explan_estimates <- model2b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_age_sensitivity")
kable(ocir_retro_model2b_explan_estimates)
ocir_retro_model2b_explan_estimates

# Regression diagnostic statistics
ocir_retro_model2b_explan_reg_stats <- model2b.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_age_sensitivity")
kable(ocir_retro_model2b_explan_reg_stats)
ocir_retro_model2b_explan_reg_stats
```

@@

### Model 2a: Disorder hierarchical, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r pcl model2a absolute whole sample}
# Regression coefficients
pcl_baseline_model2a_estimates <- model2a.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat_age_sensitivity")
kable(pcl_baseline_model2a_estimates)
pcl_baseline_model2a_estimates

# Regression diagnostic statistics
pcl_baseline_model2a_reg_stats <- model2a.reg.stats(outcome = "pcl.sum_score_base",
                                                 data_set = "dat_age_sensitivity")
kable(pcl_baseline_model2a_reg_stats)
pcl_baseline_model2a_reg_stats
```

### Model 2b: Overlapping disorders, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r pcl model2b absolute whole sample}
# Regression coefficients
pcl_baseline_model2b_estimates <- model2b.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat_age_sensitivity")
kable(pcl_baseline_model2b_estimates)
pcl_baseline_model2b_estimates

# Regression diagnostic statistics
pcl_baseline_model2b_reg_stats <- model2b.reg.stats(outcome = "pcl.sum_score_base",
                                                 data_set = "dat_age_sensitivity")
kable(pcl_baseline_model2b_reg_stats)
pcl_baseline_model2b_reg_stats
```

@@

### Model 2a: Disorder hierarchical, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r pcl model2a diff_score prepan}
# Regression coefficients
pcl_prepan_model2a_estimates <- model2a.estimates(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan_age_sensitivity")
kable(pcl_prepan_model2a_estimates)
pcl_prepan_model2a_estimates

# Regression diagnostic statistics
pcl_prepan_model2a_reg_stats <- model2a.reg.stats(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan_age_sensitivity")
kable(pcl_prepan_model2a_reg_stats)
pcl_prepan_model2a_reg_stats
```

### Model 2b: Overlapping disorders, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r pcl model2b diff_score prepan}
# Regression coefficients
pcl_prepan_model2b_estimates <- model2b.estimates(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan_age_sensitivity")
kable(pcl_prepan_model2b_estimates)
pcl_prepan_model2b_estimates

# Regression diagnostic statistics
pcl_prepan_model2b_reg_stats <- model2b.reg.stats(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan_age_sensitivity")
kable(pcl_prepan_model2b_reg_stats)
pcl_prepan_model2b_reg_stats
```

@@

### Model 2a: Disorder hierarchical, Adjusted with age^2
Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
```{r pcl model2a sum_score prepan}
# Regression coefficients
pcl_prepan_model2a_explan_estimates <- model2a.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_age_sensitivity")
kable(pcl_prepan_model2a_explan_estimates)
pcl_prepan_model2a_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model2a_explan_reg_stats <- model2a.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_age_sensitivity")
kable(pcl_prepan_model2a_explan_reg_stats)
pcl_prepan_model2a_explan_reg_stats
```

### Model 2b: Overlapping disorders, Adjusted with age^2
Model 0a + Gender_collapsed +  age^2 + Ethnicity_collapsed + Time registration and baseline
```{r pcl model2b sum_score prepan}
# Regression coefficients
pcl_prepan_model2b_explan_estimates <- model2b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_age_sensitivity")
kable(pcl_prepan_model2b_explan_estimates)
pcl_prepan_model2b_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model2b_explan_reg_stats <- model2b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_age_sensitivity")
kable(pcl_prepan_model2b_explan_reg_stats)
pcl_prepan_model2b_explan_reg_stats
```
# SENSITIVITY based on highest level of education
